---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# effective-octo-spoon

<!-- badges: start -->
<!-- badges: end -->

The goal of effective-octo-spoon is to Analyse the publicly available data on political donations to detect pattens in polical financing. 

Additionally it will use the drake package to generate a reproducible workflow for the project 

```{r setup, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
source(here::here("R/master_plan.R"))
```

There were `r readd(volume_of_donations)` donations total in the dataset

Those donations went to a huge variety of people. (`r readd(num_unique_donees)` in total)

For this analysis we will aggregate those unique recipients into all those with more than 140 donations and the remainder. This leaves us with `r nrow(readd(entity_summary))` recipients, including 'other' 
